The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-10 rational.tex
_
HOF subsection

@@

@@

\begin{multicols}{2}
    \includegraphics{diagrams/compose1.pdf}

    \includegraphics{diagrams/compose.pdf}
\end{multicols}
This is also equivalent to sequencing both the computation blocks.

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{To think about}

\item Can the operational semantics for {{langRevEE}} be an
  interpreter that is implemented in {{langRevT}} (similar to how the
  the tree traversal interpreter was implemented). This would imply
  the existence of a more powerful construction than Int, wherein the
  products would also be preserved. This is possibly worth a paper in
  itself.

\item These functions aren't really values. There is no value one can
  produce that denotes a function. These functions are the ability to
  transform a value - the possibility of transforming a value.  In the
  product encoding of environments, there is no value one can assign
  to a variable such that it denotes a function.

\begin{center}
  \includegraphics{diagrams/dispatch.pdf}
\end{center}

\item It is not fair to say that negative types flow backwards. The
  following circuits are valid in {{langRevEE}}. It is however proper
  to say that for any type {{b}} that flows in a direction, the type
  {{-b}} flows in the reverse direction.

\begin{center}
  \includegraphics{diagrams/neg_circuit1.pdf}
\end{center}

\begin{center}
  \includegraphics{diagrams/neg_circuit2.pdf}
\end{center}

@@

To summarize negative, fractional, square root, and imaginary types all make
sense. What they help you accomplish as a programmer is to disassociate
global invariants into local ones that can be satisfied independently by
subcomputations with no synchronization or communication. A computation
producing something of type $a/b$ does not need to concern itself with who is
going to supply the missing $b$: it just does its part. Conversely faced with
a complicated task, a computation might decide to break it into pieces and
demand these pieces using negative types.

>>>>

It is not fair to say that negative types flow backwards. The
following circuits are valid in {{langRevEE}}. It is however proper to
say that for any type {{b}} that flows in a direction, the type {{-b}}
flows in the reverse direction.

@@

test.

@@

\begin{multicols}{2}
\scalebox{1.1}{
    \includegraphics{diagrams/compose1.pdf}
}

\scalebox{0.8}{
    \includegraphics{diagrams/compose.pdf}
}
\end{multicols}
This is also equivalent to sequencing both the computation blocks.

@@

%% %%%%%%%%%%%%%%%%%%%%%%
%% \subsection{To think about}

%% \begin{itemize}

%% \item Can the operational semantics for {{langRevEE}} be an
%%   interpreter that is implemented in {{langRevT}} (similar to how the
%%   the tree traversal interpreter was implemented). This would imply
%%   the existence of a more powerful construction than Int, wherein the
%%   products would also be preserved. This is possibly worth a paper in
%%   itself.

%% \item 
%% \item

%% \begin{center}
%%   \includegraphics{diagrams/neg_circuit1.pdf}
%% \end{center}

%% \begin{center}
%%   \includegraphics{diagrams/neg_circuit2.pdf}
%% \end{center}

%% \end{itemize}

@@

\subsection{Higher Order Functions}

These functions aren't really values. There is no value one can
produce that denotes a function. These functions are the ability to
transform a value - the possibility of transforming a value.  In the
product encoding of environments, there is no value one can assign to
a variable such that it denotes a function.

%% \begin{center}
%%   \includegraphics{diagrams/dispatch.pdf}
%% \end{center}

\subsection{Other}
To summarize negative, fractional, square root, and imaginary types all make
sense. What they help you accomplish as a programmer is to disassociate
global invariants into local ones that can be satisfied independently by
subcomputations with no synchronization or communication. A computation
producing something of type $a/b$ does not need to concern itself with who is
going to supply the missing $b$: it just does its part. Conversely faced with
a complicated task, a computation might decide to break it into pieces and
demand these pieces using negative types.
